\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-06-20 phd-cs-us.tex
Updates from Overleaf

Graduating from top universities \emph{that we recognize} helps.
However, if committee members do not know much about schools in your country, they will likely treat your school as
\emph{``unknown foreign''}, which can be a minus point (if your school is well-known, then it is \emph{``top foreign''}, which is definitely a plus).

So what can you do about this? several things such as asking your CS dept to put itself on CSRankings (it's the easiest way to get CS people to know about the school), explaining about your school in your statement (and asking your LOR writer to do that too), and of course, if you're interested in working with Vietnamese professors, consider a PhD program in the US that  \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{have them}.

\begin{commentbox}[Vu]
Sometime PhD admission committee will share a document such as \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Foreign-Top-Schools}{this one}, which lists the top schools in several countries. Personally I have looked at Vietnamese applications (whether they are assigned to me or not) and provide input to their reviewers, e.g., X is the top tech school in Vietnam and so it should be \emph{top} instead of \emph{unknown} foreign, which makes a huge difference.
\end{commentbox}

@@

If you want to contact a prof. to \emph{ask about your admission chance}, then \textbf{don't}. We don't know, we can't answer because as explained throughout this document, we don't make individual decisions and might not even be assigned to evaluate your application.  It is the same as sending a paper draft to a journal editor and ask them if your paper will be accepted.

>>>>

Graduating from top universities \emph{that we recognize} helps. For example, if your school is well-known, then it is \emph{``top foreign''}, which is definitely a plus.
However, if committee members do not know much about schools in your country, they will likely treat your school as
\emph{``unknown foreign''}, which can be a minus point because we are uncertain about the quality of your school.

So what can you do about this? several things such as asking your CS dept to put itself on CSRankings (it's the easiest way to get CS people to know about the school) and explaining about your school in your statement (and asking your LOR writer to do that too). Of course, if you're interested in working with Vietnamese professors, consider a PhD program in the US that  \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{have them}.

\begin{commentbox}[Vu]
Sometime PhD admission committee will share a document such as \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Foreign-Top-Schools}{this one}, which lists the top schools in several countries. In some cases we ask people (faculty, students) if we think they know about the place.  For example, when I was a postdoc at UMD, people in admission committee ask me to evaluate applicants from Vietnam.  During my time at UNL and now here at GMU, I have looked at Vietnamese applications (whether they are assigned to me or not) and provide input to their reviewers, e.g., X is the top tech school in Vietnam and so it should be \emph{top} instead of \emph{unknown} foreign, which makes a huge difference.
\end{commentbox}

@@

This is one of the most common questions that international students often have. Faculty often received many mails from international students about admission, TA, RA and various related topics. Most of the time, we ignore these emails; but sometimes, we do answer them.  So under what cases we would answer and would not?

If you want to contact a prof. to \emph{ask about your admission chance}, \textbf{don't}. We don't know and can't answer because as explained throughout this document, we don't make individual decisions and might not even be assigned to evaluate your application.  It is the same as sending a paper draft to a journal editor and ask them if your paper has a chance.

So what to do if you want someone to look at your profile and give input? You could ask your professors, people at your school, or contact those who have previously applied and get feedback. For these kind of feedback,  don't ask strangers like random profs., instead ask someone you have some personal connection to.
